The Right Way to Search Evolving Graphs

### 2016-01-28 paper.tex
Explain that you should never compute with the block matrix representation

>>>>

The blocked matrix structure of the adjacency matrices presented here provide
interesting relationships between their matrix properties and the algorithmic
properties of BFS, made possible because of the reformulation of BFS as
repeated power iterations of the adjacency matrix in Algorithm~\ref{alg:bfsla}.
Note, however, that these matrices never need to be instantiated for practical
computations. Rather, since Algorithm~\ref{alg:bfsla} only requires the matrix--
vector product involving the adjacency matrix, the formulation of
Algorithm~\ref{alg:bfs} provides an efficient way to exploit the block structure
of $\bm A_n$. The $\odot$ operation provides an efficient way to compute the
action of the off-diagonal products. Representing the diagonal blocks
$A^{[t]}$ as sparse matrices product further reduces the cost of BFS by exploiting
latent sparsity in graphs that show up in practical applications.
